The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Removed the incorrect weapons of mass destructions comment and added source for silk road.

		\subsection{Tor stinks?}
			Tor is not only used by human rights activists. It is also used by distributors of illegal content and providers of illegal services, because it is deemed untraceable. This serious problem is disrupting Tor's public image. A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances, buying weapons of mass destruction and other illegal goods. The market operated as a hidden Tor service. These services are accessed through an onion address and not an IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.
			% Meer voorbeelden:
			% - international business times -> silk road (zie wikipedia)
			% - weapons of mass destruction (?)
			% Is de zin nu zo goed? Ik heb wat voorbeelden erbij gezet

>>>>

		\subsection{Tor stinks?}
			Tor is not only used by human rights activists. It is also used by distributors of illegal content and providers of illegal services, because it is deemed untraceable. This serious problem is disrupting Tor's public image. A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances and other illegal goods \cite{ibtimes2013}. The market operated as a hidden Tor service. These services are accessed through an onion address and not an IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.
			% Meer voorbeelden:
			% - international business times -> silk road (zie wikipedia)
			% - weapons of mass destruction (?)
			% Is de zin nu zo goed? Ik heb wat voorbeelden erbij gezet
